---
title: "Untitled"
author: "Sai Aditya Garlapati"
date: "3 September 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(readxl)
library(data.table)
library(dplyr)
library(ggplot2)
library(reshape2)
library(plotly)
library(tidyr)
library(gridExtra)

setwd("C:/Users/Administrator/Documents/EDA/Assignment/data-society-global-terrorism-data/original")
files <- list.files(path = "C:/Users/Administrator/Documents/EDA/Assignment/data-society-global-terrorism-data/original",pattern = ".csv")
temp <- lapply(files, fread, sep=",")
terrorist_data <- rbindlist( temp,fill=TRUE )
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output
```{r}

q1_td=terrorist_data%>%group_by(iyear)%>%summarise(No_of_Terrorist_attacks=n())


q1_ggplot=ggplot(q1_td,aes(x=iyear,y=No_of_Terrorist_attacks))+
  geom_area(fill="light blue")+
  geom_point(col="black",size=0.9)+
  geom_text(size=3,fontface='bold',
            aes(label = No_of_Terrorist_attacks),
            position = position_dodge(width = .9), vjust = -0.25)

renderPlotly(q1_ggplot)


```


